Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-19 content/contribution/R4.tex
corrected R4 section title

\begin{nestedsection}{R4: Rule-based Reasoning using Rete\dots Roar}{implementation}
	As a proof of concept, we have implemented R4: a Rule-based Reasoner for RDF-streams using Rete.
	Reasoning in R4 is performed continuously and incrementally as dataflow networks that work directly on RDF streams.
	The system architecture is shown in \reffig{R4-architecture}.
	\begin{figure}[t]
		\centering
		\includegraphics[width=0.45\textwidth]{R4-architecture}
		\caption{The system architecture of R4.}
		\labelfig{R4-architecture}
	\end{figure}

>>>>

\begin{nestedsection}{R4: Rule-based Reasoning over RDF streams using Rete}{implementation}
	As a proof of concept, we have implemented R4: a Rule-based Reasoner for RDF-streams using Rete.
	Reasoning in R4 is performed continuously and incrementally as dataflow networks that work directly on RDF streams.
	The system architecture is shown in \reffig{R4-architecture}.
	\begin{figure}[t]
		\centering
		\includegraphics[width=0.45\textwidth]{R4-architecture}
		\caption{The system architecture of R4.}
		\labelfig{R4-architecture}
	\end{figure}
